Project Review Template

### 2024-05-04 reviews/project-review-kaggwa_patrick_musta.qmd
Final Edits
Cleaned up Maunscripts, ReadMe files and deleted unnessary files

---
title: Project Review Part 5 
author: Chaohua Li
date: 04-25-2024
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

@@

Title of project: Exploring the Relationship Between β-carotene Levels, BCO1 Variants, and Atherosclerosis Progression through Data Analysis

@@

Name of project reviewer: Chaohua Li

@@

@@

The background needs to be more detailed. It would also be helpful with some citations added.

@@

* some contextualization and motivation

@@

The research question was clearly stated and explained.

@@

Data source was clearly described. There was no codebook provided.

@@

* source and overall structure of data well explained

@@

Data was well processed. Detailed comments/notes were provided for all procedures.
There was no supplementary material. The supplement qmd file in the 'manuscript' folder was from the template file.

@@

The analysis methods were appropriate for the question to be answered. Cross-validation was not used for performance evaluation. But the performance of the final was assessed on a test dataset.

@@

The results were presented in a well-structured manner. Most tables were well-formated. Maybe Table 1(summary of data) should be made more concise or moved into a supplemental material.

@@

* results are very well presented

@@

Discussion is detailed and the interpretation of results is appropriate. Strengths and limitations are specified.

@@

* strong, complete and clear discussion

@@

There are some R scripts showing up in the manuscript. And some residual content of the template needs to be removed. It would be helpful if the detailed titles/annotations can be added to the figures.

@@

The project is generally well-structured. All files are in well labeled folders. It is easy to figure out the use for each file/folder.

@@

The R scripts are well-documented with sufficient description. Each decision of analysis was justified and explained. There are residual content from template in many Rmd files(README). The qmd file for supplement material is also from the template.

@@

I was able reproduce the results. Instructions were clear.

@@

The research questions have been fully addressed. All sections are relatively complete and thorough.

@@

* strong level of thorougness

@@

Overall, this study is in good shape. The author may want to consider moving some content into a supplement file. Some R scripts show up in the manuscript, so that needs to be fixed. The residual content from template in many Rmd files also need to be cleaned.

>>>>

---
title: Project Review Template 
author: Patrick Kaggwa
date: 4-25-2024
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

@@

Title of project:Exploring the Relationship Between β-carotene Levels, BCO1 Variants, and Atherosclerosis Progression through Data Analysis (Insights into Plasma Lipid Profiles and Immune Cell Dynamics for Cardiovascular Health)

@@

Name of project reviewer: Patrick Kaggwa

@@

Write your comments and feedback below for each section/component of the project. The goal should be to help the author improve their project. Make comments as constructive and actionable as possible. You can provide both criticism and praise.

For each component, pick one summary statement by deleting the ones that do not apply and keeping only the one that you think most closely summarizes a given component.

Make sure your final document compiles/renders into a readable, well-formatted html document.

Delete any sections/text of this template that are not part of your final review document. (Including these instructions.)

@@

Overall, background demonstrates a strong contextualization of the research within the existing literature and a clear motivation for the study. Though the text is missing some references.

@@

* strong contextualization and motivation

@@

Overall, the questions and hypotheses are well-defined and directly relate to the data, providing a clear framework for the analysis and interpretation of results

@@

The data is adequately described, providing essential information about its source and structure.

@@

* source and overall structure of data somewhat explained

@@

Overall, the data cleaning and processing steps are reasonable.

@@

Overall, the analysis methods are appropriate for the data and the analysis seems to have been conducted properly. Though when during analysis some defined re sampling is not used of few observations

@@

Overall, the results are adequately presented with tables, the addition of figures and improvements in formatting and labeling could enhance readability and understanding, making the main figures and tables of publication-level quality.

@@

* results are presented ok, with room for improvement

@@

Overall, the study findings are discussed, there is room for improvement in acknowledging strengths and limitations and interpreting the findings in a more comprehensive and refined manner.

@@

* minor parts wrong, missing or unclear

@@

_The word document still has code when you render it. I think this can be improved and the document will be fine before submission._

@@

The project is well structured, folders are named well, there are few undocumented readme files

@@

The files and folders are labelled well. code is documented well and the output explained but some readme are not well decribed.

@@

Yes, the results were reproducible, code run smoothly.

@@

Overall, the study is thorough.

@@

* decent level of thoroughness

@@

_The manuscript needs to be formatted well, put applicable references in the text and improve the discussion but otherwise well done._
